Proposed Solution

### 2016-11-14 Ennan-Proposal/language.tex
stuff

There are several types of configuration 
files, and each has a different representation. Our goal is to find a good 
intermediary representation that will be language-agnostic. In general,
one could argue that the design of configuration files is pretty low 
level, and that we need a new programming language for them. We agree with 
that assertion, and actually our intermediary representation can be seen
as a new programming paradigm for writing configuration files, but this
is not the focus of this proposal. Previously, Huang {\em et al.}~\cite{huang15confvalley} proposed a 
language, ConfValley, to validate 
whether given configuration files meet administrators' specifications. 
However, ConfValley cannot check for misconfiguration checking 
capability, since it is only a library. In ConfValley the administrator 
still needs to write specifications manually, which is an error-prone
process. On the contrary, \app does not require users to manually
write anything.

>>>>

There are several types of configuration 
files, and each has a different representation. Our goal is to find a good 
intermediary representation that will be language-agnostic. In general,
one could argue that the design of configuration files is pretty low 
level, and that we need a new programming language for them. We agree with 
that assertion, and actually our intermediary representation can be seen
as a new programming language for writing configuration files, but this
is not the main focus of this proposal. Previously, Huang {\em et al.}~\cite{huang15confvalley} proposed a 
language, ConfValley, to validate 
whether given configuration files meet administrators' specifications. 
However, ConfValley cannot check for misconfiguration checking 
capability, since it is only a library. In ConfValley the administrator 
still needs to write specifications manually, which is an error-prone
process. On the contrary, \app does not require users to manually
write anything.

### 2016-11-14 Ennan-Proposal/prelim.tex
stuff

From ConfigC we drew the main inspiration for this proposal. We now briefly
outline how ConfigC works. It first automatically
analyzes a dataset of correct configuration files to derive
 rules for describing a specification. Before that process even starts,
we identified several basic types, 
such Boolean, Integer, File. With each of these types we associated a 
list of templates. We then analyze the given training data set of 
correct configuration files and derive rules describing variable                                                                                                                                                                                                                                                                                                                                                                                                                       
relations. We illustrate how is this done on two fragments of 
configuration files given in Fig.~\ref{fig:twoFiles}.  When analyzing
a file, we first assign a type to every 
keyword. After that we instantiate each type-annotated template with 
concrete keywords and we save the learned set 
of rules. For instance, with the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 
analyzing File\_1, the set of learned rules will contain the following rules:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
max_connections=300
mysql.max_persistent=200
max_connections > mysql.max_persistent
\end{lstlisting}
The set of learned rules changes with every analyzed file: contradicting 
rules are removed and new rules are added. After analyzing File\_2 the rule \texttt{max\_connections = 300} is removed. In practice, this process is done 
in parallel.

>>>>

From ConfigC we drew the main inspiration for this proposal. We now briefly
outline how ConfigC works. It first automatically
analyzes a dataset of correct configuration files to derive
 rules for describing a specification. Before that process even starts,
we identified several basic types, 
such Boolean, Integer, File. With each of these types we associated a 
list of templates. We then analyze the given training data set of 
correct configuration files and derive rules describing variable                                                                                                                                                                                                                                                                                                                                                                                                                       
relations. We illustrate how is this done on two fragments of 
configuration files given in Fig.~\ref{fig:twoFiles}. For simplicity, let us 
assume that all visible
keywords are integers. With the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 
analyzing File\_1, the set of learned rules will contain the following rules:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
max_connections=300
mysql.max_persistent=200
max_connections > mysql.max_persistent
\end{lstlisting}
The set of learned rules changes with every analyzed file: contradicting 
rules are removed and new rules are added. After analyzing File\_2 the rule \texttt{max\_connections = 300} is removed. In practice, this process is done 
in parallel.
